Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-29 paper/introduction.tex
moving extra sections to appendix

The centralized control planes of SDN, however, are not a panacea.
First, while many SDN systems provide effective \emph{intra}-domain routing
abstractions, letting users specify paths within their network,
they fail to provide a coherent means to specify preferred
\emph{inter}-domain routes. 
This means that existing inter-domain routing protocols and their associated configuration difficulties will be around for the forseeable future.
\ryan{I added this. Is it true? what about SDX?}
\todd{What is the impact of these
  languages not supporting inter-domain routing?  How are those
  policies expressed instead in an SDN context?  A sentence on the
  impact would help.}  
Second, centralized control planes
require careful design and engineering to be robust to failures---one must ensure that all devices can communicate with the controller at all times, even under arbitrary combinations of failure. Even ignoring failures, it is necessary for controller systems to
scale to meet the demands of large, geographically distributed networks,
and to react quickly
to a changing environment. To address this challenge, researchers are exploring
multi-controller systems with interacting controllers, thus bringing back distributed
control planes~\cite{mccauley2013extending,onos} and their current programming difficulties.
%However, academic
%language design and implementation efforts have not kept pace.  For instance, work on many
%experimental SDN languages~\cite{frenetic,flowlog,vericon,merlin,netkat,kinetic,pga} has not yet shown how to implement fault tolerant
%multi-controller systems that support their high-level abstractions efficiently.

>>>>

The centralized control planes of SDN, however, are not a panacea.
First, while many SDN systems provide effective \emph{intra}-domain routing
abstractions, letting users specify paths within their network,
they fail to provide a coherent means to specify preferred
\emph{inter}-domain routes.  
Second, centralized control planes
require careful design and engineering to be robust to failures---one must ensure that all devices can communicate with the controller at all times, even under arbitrary combinations of failure. Even ignoring failures, it is necessary for controller systems to
scale to meet the demands of large, geographically distributed networks,
and to react quickly
to a changing environment. To address this challenge, researchers are exploring
multi-controller systems with interacting controllers, thus bringing back distributed
control planes~\cite{mccauley2013extending,onos} and their current programming difficulties.
%However, academic
%language design and implementation efforts have not kept pace.  For instance, work on many
%experimental SDN languages~\cite{frenetic,flowlog,vericon,merlin,netkat,kinetic,pga} has not yet shown how to implement fault tolerant
%multi-controller systems that support their high-level abstractions efficiently.
